Polynomial phase estimation by least squares phase unwrapping

### 2013-12-16 paper.tex
added minor

This section describes the results of Monte-Carlo simulations with the least squares unwrapping (LSU) estimator, the high order ambiguity function (HAF) estimator~\cite{Peleg_DPT_1995}, the product high order ambiguity function (PHAF) estimator~\cite{Barbarossa_PHAF_1998}, the cubic phase function (CPF) estimator~\cite{Oshea_cpf_2004} and the estimators that result from combining the HAF and CPF~\cite{Djurovic_haf_cpf_2012}.  The CPF estimator only applies to polynomial phase signals of order $m=3$ and when the number of observations $N$ is odd.  In all simulations the unknown amplitude is $\rho = 1$ and $N = 199$.  The $X_1, \dots, X_N$ are pseudorandomly generated independent and identically distributed circularly symmetric complex Gaussian with variance $\expect\abs{X_1}^2 = \sigma_c^2$.  The corresponding signal to noise ratio (SNR) is $\rho^2 \sigma_c^{-2} = \sigma_c^{-2}$.  The number of replications of each Monte-Carlo experiment is $T = 2000$ to obtain estimates $\widehat{\mubf}_1, \dots, \widehat{\mubf}_T$ and the corresponding dealiased errors $\widehat{\lambdabf}_t = \dealias(\tilde{\mubf} - \widehat{\mubf}_t)$ are computed.  The sample mean square error (MSE) of the $k$th coefficient is computed according to $\tfrac{1}{T}\sum_{t=1}^T \widehat{\lambda}_{k,t}^2$ where $\widehat{\lambda}_{k,t}$ is the $k$th element of $\widehat{\lambdabf}_t$.  In all simulations four \emph{lag sets} are used for the PHAF estimator~\cite{Barbarossa_PHAF_1998} and the LSU estimator is approximated using the $K$-best method described in Section~\ref{sec:lattice-theory}.  The maximum number of branches allowed is $K=20N$.  The arithmetic complexity of the LSU estimator is $O(N^3\log N)$ in this case.

@@

Figure~\ref{plot:m5} displays the sample MSE of the highest order coefficient $\mu_5$  for a polynomial phase signal of order $m=5$.  In this case the LSU and PHAF estimators reach a threshold at \unit[12]{dB}, the HAF estimator at \unit[18]{dB}, the estimator that combines the CPF and HAF at \unit[10]{dB}, and the product form of this estimator (PCH) at \unit{6}[dB] (see~\cite[Section~5.A]{Djurovic_haf_cpf_2012}).  In this figure the true coefficients are $\tilde{\mubf} = \left[ \tfrac{1}{4}, \tfrac{1}{4}, \tfrac{1}{8N}, \tfrac{1}{24N^2}, \tfrac{1}{96N^3}, \tfrac{1}{480N^4}  \right]$ and these are chosen specifically to satisfy the requirement of the HAF, PHAF, CPF-HAF and PCH estimators.  As in the case where $m=3$, the region of coefficients suitable for the HAF, PHAF, CPF-HAF and PCH estimators is much smaller than the identifiable region.  The effect becomes more severe as $m$ increases.  When $m=5$ and $N=199$ the space of coefficients searched by these estimators is approximately $10^{-16}$ the size of the identifiable region.  This is a dramatic reduction in the range of detectable polynomial phase signals. Figure~\ref{plot:m5big} displays results under the same conditions as Figure~\ref{plot:m5} but with $\tilde{\mubf} = \left[\tfrac{1}{4}, \tfrac{1}{4}, \tfrac{1}{8}, \tfrac{1}{24}, \tfrac{1}{96}, \tfrac{1}{480}  \right]$.  The conclusion is similar to that from Figure~\ref{plot:m3big}.  The performance of the LSU estimator remains unchanged, but the HAF, PHAF, CPF-HAF and PCH estimators fail completely.  The Zhou and Wang estimator can again be used to increase the range of parameters for the HAF, but simulations indicate that the threshold for the estimator is approximately~\unit[103]{dB}.

>>>>

This section describes the results of Monte-Carlo simulations with the least squares unwrapping (LSU) estimator, the high order ambiguity function (HAF) estimator~\cite{Peleg_DPT_1995}, the product high order ambiguity function (PHAF) estimator~\cite{Barbarossa_PHAF_1998}, and the cubic phase function (CPF) estimator~\cite{Oshea_cpf_2004}.  Simulation are also performed with two recently proposed estimators that combine the HAF and CPF~\cite{Djurovic_haf_cpf_2012}.  The standard version of this estimator we refer to using the abreviation CPF-HAF~\cite[Sectoion~3]{Djurovic_haf_cpf_2012} and the product form of the estimator we abreviate by PCH~\cite[Section~5.A]{Djurovic_haf_cpf_2012}.  The CPF estimator only applies to polynomial phase signals of order $m=3$ and when the number of observations $N$ is odd.  In all simulations the unknown amplitude is $\rho = 1$ and $N = 199$.  The $X_1, \dots, X_N$ are pseudorandomly generated independent and identically distributed circularly symmetric complex Gaussian with variance $\expect\abs{X_1}^2 = \sigma_c^2$.  The corresponding signal to noise ratio (SNR) is $\rho^2 \sigma_c^{-2} = \sigma_c^{-2}$.  The number of replications of each Monte-Carlo experiment is $T = 2000$ to obtain estimates $\widehat{\mubf}_1, \dots, \widehat{\mubf}_T$ and the corresponding dealiased errors $\widehat{\lambdabf}_t = \dealias(\tilde{\mubf} - \widehat{\mubf}_t)$ are computed.  The sample mean square error (MSE) of the $k$th coefficient is computed according to $\tfrac{1}{T}\sum_{t=1}^T \widehat{\lambda}_{k,t}^2$ where $\widehat{\lambda}_{k,t}$ is the $k$th element of $\widehat{\lambdabf}_t$.  In all simulations four \emph{lag sets} are used for the PHAF and PCH estimators~\cite{Barbarossa_PHAF_1998,Djurovic_haf_cpf_2012} and the LSU estimator is approximated using the $K$-best method described in Section~\ref{sec:lattice-theory}.  The maximum number of branches allowed is $K=20N$.  The arithmetic complexity of the LSU estimator is $O(N^3\log N)$ in this case.

@@

Figure~\ref{plot:m5} displays the sample MSE of the highest order coefficient $\mu_5$  for a polynomial phase signal of order $m=5$.  In this case the LSU and PHAF estimators reach a threshold at \unit[12]{dB}, the HAF estimator at \unit[18]{dB}, the estimator that combines the CPF and HAF at \unit[10]{dB}, and the product form of this estimator (PCH) at \unit[6]{dB} (see~\cite[Section~5.A]{Djurovic_haf_cpf_2012}).  In this figure the true coefficients are $\tilde{\mubf} = \left[ \tfrac{1}{4}, \tfrac{1}{4}, \tfrac{1}{8N}, \tfrac{1}{24N^2}, \tfrac{1}{96N^3}, \tfrac{1}{480N^4}  \right]$ and these are chosen specifically to satisfy the requirement of the HAF, PHAF, CPF-HAF and PCH estimators.  As in the case where $m=3$, the region of coefficients suitable for the HAF, PHAF, CPF-HAF and PCH estimators is much smaller than the identifiable region.  The effect becomes more severe as $m$ increases.  When $m=5$ and $N=199$ the space of coefficients searched by these estimators is approximately $10^{-16}$ the size of the identifiable region.  This is a dramatic reduction in the range of detectable polynomial phase signals. Figure~\ref{plot:m5big} displays results under the same conditions as Figure~\ref{plot:m5} but with $\tilde{\mubf} = \left[\tfrac{1}{4}, \tfrac{1}{4}, \tfrac{1}{8}, \tfrac{1}{24}, \tfrac{1}{96}, \tfrac{1}{480}  \right]$.  The conclusion is similar to that from Figure~\ref{plot:m3big}.  The performance of the LSU estimator remains unchanged, but the HAF, PHAF, CPF-HAF and PCH estimators fail completely.  The Zhou and Wang estimator can again be used to increase the range of parameters for the HAF, but simulations indicate that the threshold for the estimator is approximately~\unit[103]{dB}.
